\documentclass[11pt,a4paper]{report}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows.meta,positioning,fit}

\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}

\lstdefinestyle{bash}{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  backgroundcolor=\color{gray!8}
}

\title{CXR Kubernetes Deployment Manual\\
\large Bootcamp workflow: Terraform, kind, Helm, and Argo CD}
\author{CXR Ops Lab --- \texttt{cxr-ops-lab}}
\date{2026-05-28}

\begin{document}
\maketitle
\begin{abstract}
This manual documents the end-to-end Kubernetes deployment path used for the CXR bootcamp:
local \textbf{kind} cluster \texttt{cxr-lab}, Docker image \texttt{cxr-ui:local}, Helm chart
\texttt{helm/cxr-ui}, optional Terraform provisioning, and Argo CD GitOps from
\textbf{GitHub} (\texttt{UdonsiKalu/cxr-ops-lab}). It explains rationale, folder layout,
commands, ports, CI vs.\ CD, and how to adapt the pattern to another environment.
\end{abstract}
\tableofcontents
\newpage

\chapter{Executive summary}

\section{What you built}
\begin{itemize}
  \item A \textbf{local Kubernetes lab} (\texttt{kind} / \texttt{cxr-lab}) running the rehearsal CXR UI.
  \item \textbf{Helm (SW.4)} packages the app as chart \texttt{cxr-ui}.
  \item \textbf{Terraform (SW.5)} can reproducibly ensure the kind cluster exists.
  \item \textbf{Argo CD (SW.8)} is \textbf{continuous delivery}: Git on GitHub is the source of truth; Argo syncs the Helm chart into the cluster.
  \item \textbf{CI} (build/test/Trivy) lives in \texttt{cxr-ui-rehearsal} --- it does \textbf{not} deploy to this kind cluster.
\end{itemize}

\section{One-line flow}
\begin{center}
\textbf{Build image} $\rightarrow$ \textbf{Load into kind} $\rightarrow$ \textbf{Helm deploy} $\rightarrow$ \textbf{Argo keeps Git = cluster} $\rightarrow$ \textbf{Browser via port-forward}
\end{center}

\section{URLs (lab)}
\begin{center}
\begin{tabular}{ll}
\toprule
URL & Meaning \\
\midrule
\texttt{http://localhost:8251} & Daily dev (full analyze) \\
\texttt{http://localhost:3000} & Docker Compose lab (SW.2) \\
\texttt{http://localhost:8081} & K8 UI (port-forward to pod :3000) \\
\texttt{https://localhost:8083} & Argo CD UI \\
\bottomrule
\end{tabular}
\end{center}

\chapter{Rationale: why each layer exists}

\section{Design principles}
\begin{enumerate}
  \item \textbf{Do not touch production} \texttt{cxrlabs-dev/platform/infra}.
  \item \textbf{Same app image path} as SW.1 Docker: rehearsal \texttt{cxr-ui} built into \texttt{cxr-ui:local}.
  \item \textbf{Learn K8 mechanics} (namespace, deployment, service) before GitOps polish.
  \item \textbf{Helm} parameterizes the chart (image tag, replicas, env) for SW.4.
  \item \textbf{Terraform} documents reproducible cluster creation (SW.5 ADR: local kind only for bootcamp).
  \item \textbf{Argo CD} implements SW.8 GitOps: push chart changes $\Rightarrow$ cluster reconciles.
\end{enumerate}

\section{CI vs.\ CD (critical distinction)}
\begin{center}
\begin{tikzpicture}[
  node distance=1.2cm,
  box/.style={draw, rounded corners, minimum width=3.2cm, minimum height=0.9cm, align=center, font=\small}
]
  \node[box] (git) {Git push};
  \node[box, right=of git] (ci) {CI\\\texttt{cxr-ui-rehearsal}\\build, Playwright, Trivy};
  \node[box, below=of git] (gitops) {Git push\\\texttt{cxr-ops-lab}};
  \node[box, right=of gitops] (argo) {CD --- Argo CD\\sync \texttt{helm/cxr-ui}};
  \node[box, right=of argo] (k8) {kind cluster\\\texttt{cxr-lab}};
  \draw[-{Stealth}] (git) -- (ci);
  \draw[-{Stealth}] (gitops) -- (argo) -- (k8);
\end{tikzpicture}
\end{center}

\textbf{Push-based CD} (GitHub Actions runs \texttt{helm upgrade}) is a valid alternative but \textbf{not wired} for this home lab because the cluster is local, the image is \texttt{cxr-ui:local} loaded via \texttt{kind load}, and the syllabus target for CD is Argo.

\chapter{Repository and folder map}

\section{\texttt{cxr-ops-lab} layout (canonical)}
\begin{lstlisting}[style=bash,basicstyle=\ttfamily\footnotesize]
cxr-ops-lab/
  Dockerfile              # SW.1 image (cxr-ui:local)
  Dockerfile.compose      # SW.2 (not used in K8 pod by default)
  helm/cxr-ui/            # SW.4 Helm chart (Argo source path)
    Chart.yaml
    values.yaml
    templates/
  k8s/                    # SW.3 raw manifests (study / --raw)
    namespace.yaml
    deployment.yaml
    service.yaml
    argocd/
      application-cxr-ui.yaml
  terraform/              # SW.5 kind provisioner
  scripts/
    00-install-tools.sh   # kind, kubectl, helm, terraform, argocd
    01-kind-cluster.sh
    02-build-and-load.sh
    03-k8-up.sh           # one-shot cluster+image+helm
    05-helm-install.sh
    12-k8-ensure.sh
    13-argo-install.sh
    14-stack-test.sh
    15-e2e-deploy.sh      # full stack
  evidence/               # SW.3, SW.4, SW.8 proof
  docs/                   # this manual
  bin/                    # downloaded CLIs (gitignored)
\end{lstlisting}

\section{Related repos (not merged)}
\begin{itemize}
  \item \textbf{App source:} \texttt{cxr-ui-prune-rehearsal/cxr-ui} (build context for Dockerfile).
  \item \textbf{CI:} \texttt{https://github.com/UdonsiKalu/cxr-ui-rehearsal}.
  \item \textbf{Ops + Helm + Argo:} \texttt{https://github.com/UdonsiKalu/cxr-ops-lab} (private).
  \item \textbf{Production (untouched):} \texttt{cxrlabs-dev/claim\_analysis\_tools/platform/infra}.
\end{itemize}

\chapter{Architecture diagrams}

\section{End-to-end deployment flow}
\begin{center}
\begin{tikzpicture}[
  node distance=0.55cm and 0.4cm,
  step/.style={draw, rounded corners, fill=blue!8, minimum width=2.8cm, minimum height=0.75cm, align=center, font=\scriptsize},
  infra/.style={draw, rounded corners, fill=orange!12, minimum width=2.8cm, minimum height=0.75cm, align=center, font=\scriptsize}
]
  \node[step] (tf) {SW.5 Terraform\\or 01-kind-cluster};
  \node[step, right=of tf] (build) {SW.1 02-build-and-load\\cxr-ui:local};
  \node[step, right=of build] (helm) {SW.4 05-helm-install\\Helm release};
  \node[step, right=of helm] (argo) {SW.8 13-argo-install\\Argo Application};
  \node[infra, below=1.2cm of build] (kind) {kind cluster cxr-lab};
  \node[infra, below=of helm] (pod) {Pod cxr-ui :3000};
  \node[infra, below=of argo] (pf) {Host :8081 port-forward};
  \draw[-{Stealth}] (tf) -- (kind);
  \draw[-{Stealth}] (build) -- (kind);
  \draw[-{Stealth}] (helm) -- (pod);
  \draw[-{Stealth}] (argo) -- (pod);
  \draw[-{Stealth}] (pod) -- (pf);
\end{tikzpicture}
\end{center}

\section{In-cluster object graph (Argo tree)}
\begin{center}
\begin{tikzpicture}[
  node distance=1cm,
  res/.style={draw, rounded corners, minimum width=2.2cm, minimum height=0.6cm, align=center, font=\small}
]
  \node[res] (app) {Application cxr-ui};
  \node[res, below=of app] (ns) {Namespace cxr-ui};
  \node[res, below left=0.8cm and 0.2cm of ns] (svc) {Service cxr-ui};
  \node[res, below right=0.8cm and 0.2cm of ns] (dep) {Deployment cxr-ui};
  \node[res, below=of dep] (rs) {ReplicaSet};
  \node[res, below=of rs] (pod) {Pod 1/1 Running};
  \draw[-{Stealth}] (app) -- (ns);
  \draw[-{Stealth}] (ns) -- (svc);
  \draw[-{Stealth}] (ns) -- (dep);
  \draw[-{Stealth}] (dep) -- (rs) -- (pod);
\end{tikzpicture}
\end{center}

\section{Dependencies (M4.8): out of cluster}
SQL, Qdrant, and Python analyzers stay on the host or Compose stack in the bootcamp K8 pod. Full Claim Studio analyze uses \texttt{:8251} or \texttt{:3000}, not the K8 UI shell alone.

\chapter{Step-by-step: run from zero}

\section{Prerequisites}
Docker, Git, optional \texttt{gh} for private repo auth. Install CLIs:
\begin{lstlisting}[style=bash]
cd /path/to/cxr-ops-lab
./scripts/00-install-tools.sh
export PATH="$PWD/bin:$PATH"
\end{lstlisting}

\section{Option A --- Full end-to-end (recommended)}
\begin{lstlisting}[style=bash]
./scripts/15-e2e-deploy.sh
# Terraform apply -> 12-k8-ensure -> 13-argo-install -> port-forwards -> 14-stack-test
\end{lstlisting}

\section{Option B --- Manual layers}
\begin{lstlisting}[style=bash]
# SW.5 / cluster
cd terraform && terraform init && terraform apply && cd ..
# SW.1 + load
./scripts/02-build-and-load.sh
# SW.4
./scripts/05-helm-install.sh
# SW.8
export CXR_ARGO_REPO_URL=https://github.com/UdonsiKalu/cxr-ops-lab.git
./scripts/13-argo-install.sh
# Access
kubectl port-forward -n cxr-ui svc/cxr-ui 8081:3000 --address=127.0.0.1
kubectl port-forward -n argocd svc/argocd-server 8083:443 --address=127.0.0.1
\end{lstlisting}

\section{Argo CD login}
\begin{lstlisting}[style=bash]
kubectl -n argocd get secret argocd-initial-admin-secret \
  -o jsonpath='{.data.password}' | base64 -d; echo
# User: admin  |  URL: https://localhost:8083
\end{lstlisting}

\section{Verify}
\begin{lstlisting}[style=bash]
./scripts/14-stack-test.sh
kubectl get application cxr-ui -n argocd
helm list -n cxr-ui
curl -s -o /dev/null -w '%{http_code}\n' http://127.0.0.1:8081/
\end{lstlisting}

\chapter{Helm and GitOps workflow}

\section{Helm role}
Helm is the \textbf{package manager}: \texttt{helm/cxr-ui/values.yaml} sets image tag, replicas, env; templates render Deployment/Service/Namespace.

\section{Day-to-day change loop}
\begin{enumerate}
  \item Edit \texttt{helm/cxr-ui/values.yaml} (or templates).
  \item \texttt{git commit \&\& git push} to \texttt{cxr-ops-lab}.
  \item Argo Application \texttt{cxr-ui} syncs (auto-sync enabled).
  \item Confirm in Argo UI: \textbf{Synced / Healthy}.
  \item Open \texttt{http://localhost:8081} (if port-forward running).
\end{enumerate}

\section{What is not ``set and forget''}
\begin{itemize}
  \item kind cluster may be stopped to save CPU.
  \item Image \texttt{cxr-ui:local} must be rebuilt and \texttt{kind load} after app changes.
  \item Port-forwards are not in Kubernetes --- restart or use \texttt{cxr-k8-forward.service}.
\end{itemize}

\chapter{Script reference}

\begin{longtable}{@{}p{3.6cm}p{9.8cm}@{}}
\toprule
Script & Purpose \\
\midrule
\endhead
\texttt{00-install-tools.sh} & Install kind, kubectl, helm, terraform, argocd into \texttt{bin/}. \\
\texttt{01-kind-cluster.sh} & Create \texttt{cxr-lab} if missing. \\
\texttt{02-build-and-load.sh} & Build \texttt{cxr-ui:local} from rehearsal UI; load into kind. \\
\texttt{03-k8-up.sh} & One-shot: cluster + build/load + Helm. \\
\texttt{05-helm-install.sh} & \texttt{helm upgrade --install cxr-ui}. \\
\texttt{12-k8-ensure.sh} & Idempotent: start kind, load image, Helm upgrade. \\
\texttt{13-argo-install.sh} & Install Argo CD; repo secret; Application from GitHub. \\
\texttt{14-stack-test.sh} & Integration test (terraform, helm, argo, HTTP probes). \\
\texttt{15-e2e-deploy.sh} & Orchestrates full stack. \\
\bottomrule
\end{longtable}

\chapter{Adapting to another deployment}

\section{Checklist}
\begin{enumerate}
  \item Fork or clone \texttt{cxr-ops-lab}; set \texttt{CXR\_UI\_SRC} to your app path.
  \item Replace \texttt{kind} with cloud cluster OR keep kind for dev.
  \item Use a \textbf{container registry} (GHCR/ECR): build, push, set \texttt{values.yaml} \texttt{image.repository} and \texttt{tag}.
  \item Update Argo \texttt{CXR\_ARGO\_REPO\_URL} and private repo credentials.
  \item Replace port-forward with \textbf{Ingress} or cloud LoadBalancer.
  \item Wire SQL/Qdrant via in-cluster services, ExternalName, or env (see M4.8 diagram).
  \item Optional: add GitHub Actions job for \texttt{helm upgrade} (push-based CD) instead of or alongside Argo.
\end{enumerate}

\section{Syllabus mapping}
\begin{center}
\begin{tabular}{ll}
\toprule
Syllabus & Artifact \\
\midrule
SW.1 & \texttt{Dockerfile}, \texttt{cxr-ui:local} \\
SW.2 & Compose (parallel, :3000) \\
SW.3 & \texttt{k8s/}, kind, :8081 \\
SW.4 & \texttt{helm/cxr-ui/} \\
SW.5 & \texttt{terraform/} \\
SW.8 & Argo CD + \texttt{k8s/argocd/} \\
\bottomrule
\end{tabular}
\end{center}

\chapter{Troubleshooting}

\begin{itemize}
  \item \textbf{:8081 refused} --- start kind node; run \texttt{12-k8-ensure.sh}; start port-forward.
  \item \textbf{Argo OutOfSync / private repo} --- ensure \texttt{repo-cxr-ops-lab} secret + \texttt{gh auth token}.
  \item \textbf{Helm adopt error} --- \texttt{05-helm-install.sh} adopts namespace from raw kubectl apply.
  \item \textbf{Analyze fails on :8081} --- expected; use :8251 or :3000 Compose for full analyze.
  \item \textbf{ImagePullBackOff} --- kind needs \texttt{kind load docker-image cxr-ui:local}.
\end{itemize}

\chapter{Evidence and further reading}

\begin{itemize}
  \item \texttt{evidence/SW3-k8-evidence.md}, \texttt{SW4-helm-verify-2026-05-28.md}, \texttt{SW8-e2e-stack-2026-05-28.md}
  \item \texttt{docs/K8-DEPLOY.md}, \texttt{docs/ADR-SW5-terraform-kind.md}
  \item GitHub: \url{https://github.com/UdonsiKalu/cxr-ops-lab}
\end{itemize}

\end{document}
